---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# hivstr

<!-- badges: start -->
<!-- badges: end -->

The goal of hivstr is to bypass using the Kenya HIV self-testing distribution channels, a category combination, directly from the analytic views, making it easier to relate the HIV self-testing data on a single chart/table. 

## Installation

hivstr is on its way to [CRAN](https://CRAN.R-project.org). You can install the released version of hivstr from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("hivstr")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("psi-mis/hivstr")
```
## Usage

Load the package with:

```{r}
library(hivstr)

```

Then set and pass credentials to a PSI MIS. 

```{r}
# server url, default is clone
baseurl <- "https://clone.psi-mis.org/"

# enter username & password
usr <- "ke_tunza"
pwd <- "#"

# login to a PSI MIS
#api_basic_auth(baseurl = baseurl, username = usr, password = pwd)

```

Run this function to bypass HIVST KE distribution channels:

```{r,}

#bypass_ke_distr(baseurl)

```

Alternatively, please download the scripted file [here](https://github.com/psi-mis/hivstr/blob/main/ke_hivst-script.R) and source it from your R CMD like this: 

```{r, eval=FALSE}
source("~ the location of the script")
```

